%------------------------------------------------------------------------------
\chapter{Acknowledgements}
\label{sec:ack}
%------------------------------------------------------------------------------

The realisation of the present work has been made possible through
valuable assistance, counsels and contributions of experts and
collaborators to whom I feel myself obliged to pay my sincere
gratitudes.

First of all, I would like to pay my most heartfelt tributes to my ,
Günther Dissertori, for providing me with the opportunity to pursue my
PhD studies in physics at the ETH Zürich. I will never forget the
unrelenting and precious support, guidance and comments.


My acknowledgement and appreciations go to Dominik Dannheim, as well,
who in capacity as my supervisor at CERN, oversaw my work during three
years of close collaboration, through exertion of notable care and
skill in monitoring the Research Project on the Vertex Detector R\&D.

I have to offer my unqualified and heartfelt gratitude to Lucie
Linssen, as the group leader of the EP-LCD group, who never hesitated
to provide me with excellent and invaluable opportunities to work in
her dynamic and creative group at CERN and for her encouragements to
pursue and fulfill my PhD studies.

I owe a lot to the EP-LCD group in general for their contribution to
my work and also all the memorable time we have shared during
gatherings lunches, coffee breaks and social events. More
particularly, I express my gratitude to:

\begin{itemize}
\item Andreas Nurnberg, who always was present for providing his
  counsel and advice and all his help and patience for reading
  meticulously my thesis and giving me instructive comments and
  drawing conclusions.

\item The Medipix collaboration, especially Messrs. Michael Campbell,
  Xavi Llopart Cudie and Jérôme Alozy for guidance and advice about
  the Timepix chips.

\item Daniel Hynds and Adrian Fiergolski for the various discussions
  and test-beams we have shared.

\item Mathieu Benoît for leading me to the pixel world through
  test-beams, TCAD simulations and AllPix simulations.

\item Rosa Simoniello, for sharing the office and all the discussions
  and laughs we have shared.
\end{itemize}

I would like to thank my friends with whom I have shared great
memorable moments and I could count on them for any kind of
support. My friends from Lausanne whom I met during my studies at EPFL
and we shared many years on the university benches and now we share so
many great events: Charlotte, Chloé, Christophe, Coralie, Lara, Mina,
Salim and Sebastien. And to my friends I have met at CERN: Elena,
Enrico, Luca, Milena and Myriam.

Finally, I would like to thank my amazing family: my parents,
Mahmanzar and Behzad, for their unconditional love and support
throughout all my life, for all their sacrifices without which I could
not imagine where I would be now. My beloved sister and housemate,
Yassaman, for always being present, encouraging me and tolerating me
during the times I was low (basically the whole year of 2016). My
beloved sister and brother, Yassaman and Alireza, for always being
present by my side and encouraging me.

% I would like to thank ...

% You should probably use \texttt{\textbackslash chapter*} for
% acknowledgements at the beginning of a thesis and
% \texttt{\textbackslash chapter} for the end.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End: 
